Optimal (Multiway) Spatial Joins

### 2024-05-30 msj.tex
yufei

First, we prove that $h$ crosses $r'$. It suffices to show that $\xleft(h)  < x_1 \leq x_2 < \xright(h)$ and $y_h \in [y_1, y_2]$. Both conditions are satisfied since $h$ crosses $r^* = [x_1,x_2]\times [y_1, \maxtop(r')]$, and $\maxtop(r')\leq y_2$.

@@

Then, we prove that $h$ crosses $B_{\bm{t}}$. It suffices to show that $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$ and $y_h \in [y_1, \ytop(B_{\bm{t}})]$.
\begin{itemize}
    \item Since $h$ crosses $r'$, we have $\xleft(h) < x_1 \leq x_2 < \xright(h)$. Since $r' = \gbot(B_{\bm{t}})$, we have the x-range of $B_{\bm{t}}$ is contained in $[x_1,x_2]$. Therefore, $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$.
    \item Since $h$ crosses $r^*$, we have $y_h \in [y_1, \maxtop(r')]$. By the definition of $h$, we have $y_h \leq \ytop(B_{\bm{t}})$. Therefore, $y_h \in [y_1, \ytop(B_{\bm{t}})]$.
\end{itemize}

>>>>

We first show that $h$ crosses $r'$, or equivalently: $\xleft(h)  < x_1 \leq x_2 < \xright(h)$ and $y_h \in [y_1, y_2]$. These conditions hold true because $h$ crosses $r^* = [x_1,x_2]\times [y_1, \maxtop(r')]$, and $\maxtop(r')\leq y_2$ (due to the definition of top-sliced rectangle in \eqref{eqn:hv:type1:topsliced}).

@@

Finally, we show that $h$ crosses $B_{\bm{t}}$, or equivalently: $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$ and $y_h \in [\ybot(B_\bm{t}), \ytop(B_{\bm{t}})] = [y_1, \ytop(B_{\bm{t}})]$.
\begin{itemize}
    \item The fact of $h$ crossing $r'$ tells us $\xleft(h) < x_1 \leq x_2 < \xright(h)$. Since $r' = \gbot(B_{\bm{t}})$, we have the x-range of $B_{\bm{t}}$ is contained in $[x_1,x_2]$. Therefore, $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$.
    \item Since $h$ crosses $r^*$, we have $y_h \in [y_1, \maxtop(r')]$. By the definition of $h$, we have $y_h \leq \ytop(B_{\bm{t}})$. Therefore, $y_h \in [y_1, \ytop(B_{\bm{t}})]$.
\end{itemize}
